---
title: "Reltrad in the United States, 1972 - 2016"
slug: "Reltrad in the US"
author: "David Eagle, PhD"
date: "2019-01-15"
output:
  html_document: default
  pdf_document: default
categories:
- Measuring religion
- R
bibliography: /Users/dee4/Box Sync/Projects/BibTexFile/MyLibrary.bib
---

## Religious Affiliation According to *Reltrad*
### How the United States has Changed Religiously 1972-2016

In a previous [post](https://www.davideagle.org/post/reltrad-r/) I generated the code to create the *reltrad* variable in the General Social Survey. In this post, I use that code to plot how religious affiliation has changed in the United States.

In the R code below, I use the package [*srvyr*](https://cran.r-project.org/web/packages/srvyr/srvyr.pdf) to use *dplyr*-like syntax to create a weighted survey object. 

```{r, echo = T, message = F, warning = F }
source("ReltradGSS.R")
library(tidyverse)
library(srvyr)
as.numeric.factor <- function(x) {as.numeric(levels(x))[x]}

gssSvy <-  gss %>%  as_survey_design(ids = 1, weights = wtss)

relTable = gssSvy %>% group_by(year, reltrad) %>%
  summarize(proportion = survey_mean(na.rm=T))

relTable$year = as.numeric.factor(relTable$year)

relTable = relTable %>% mutate(ymin = proportion - 1.96*proportion_se,
                               ymax = proportion + 1.96*proportion_se)

relTable$reltrad <- factor(relTable$reltrad, levels = 
                             c("Roman Catholic", "Mainline Protestant",
                               "Conservative Protestant", "None",
                               "Other", "Black Protestant"),
                            labels =
                             c("Roman Catholic", "Mainline Protestant",
                               "Conservative Protestant", "None",
                               "Other", "Black Protestant"))
```

Now, using the magic of *ggplot2* I generate a plot of how religious affiliation has changed in the United States from 1972 to 2016. 

```{r}
ggplot(data = relTable, aes(x=year, y=proportion, ymin = ymin, ymax = ymax, color = reltrad)) + 
  geom_ribbon(alpha = .2, linetype = 0) + geom_point() + geom_line() + 
  ylab("") + xlab("") +
  scale_x_continuous(limits=c(1970, 2020)) + 
  scale_y_continuous(limits=c(0, .45)) + 
  scale_color_discrete("Reltrad")+
  theme_light() + 
 labs(title = "1972-2016, Nones are on the rise, Christians on the Decline", 
      subtitle = "(Proportion)",
      caption = "Source: General Social Survey, 1972-2016")  
```

A few notable trends are evident in this plot. First of all, the proportion of Roman Catholics in the United States has declined rapidly over this period. From a a high of about 45% of the US population, the proportion of Catholics sank to about 25% in mid 1990s. Due to Latin American immigration, the proportion of Catholics have increased since the 1990s to about 30%.

Second, there has been a very steep rise in the number of people claiming no religious affiliation. Non-affliates were a pretty steady 8% of the US population from the early 1970s to the early 1990s. The proportion of nones has climbed steeply since then, reaching a high of 25% of the US population, making them the second largest "religious" group in the United States.

Third, there is some strangeness in these data from the mid-1980s to the mid-1990s. Over this period, there is a fairly large increase in the proportion of the population classified as Mainline Protestant. It is not clear if this is a problem with the denominational classification system in the GSS or if it reflects real growth. My suspicion is that this is an issue with the way denomination was coded over this period and not a real increase in the proportion of Mainline Protestants in the US.
 
Also important is that the "Other" religion category is steadily climbing, and has reached a high of about 5% of the US population. Conservative Protestants also seem to be on the decline. In the last two waves of the GSS they are at an all-time low of about 18%. 

