\newcommand{\Revision}{\textit{under revision}}
\newcommand{\CS}{*} % corresponding author
\newcommand{\CF}{\textsuperscript{\#}} % co-first author

\section*{Peer-reviewed Publications}
\CS corresponding author, \CF co-first author.

\begin{enumerate}
\item Hamm, A., \&  \Eagle. (2021). ``Clergy Who Leave Pastoral Ministry: A Review of the Literature.'' Forthcoming in the \textit{Journal of Psychology and Theology}.

\item \Eagle, Rash, J., Tice, L., \& Proeschold-Bell, R.J. (2021). ``Evaluating the online delivery of the Trier Social Stress Test.'' Forthcoming in the \textit{International Journal of Psychophysiology}.

\item Hybels, C.F., Blazer, D.G., \Eagle, \& Proeschold-Bell, R.J. (2020). ``Age differences in trajectories of depressive, anxiety and burnout symptoms in a population with a high likelihood of persistent occupational distress.'' \emph{International Psychogeriatrics}. Online ahead of print. \doi{10.1017/S1041610220001751}\

\item Liu, X., Whetten, K., Prose, N.S., \Eagle, Parnell, H.E., Amanya, C., Vann, V., Dubie, M.E., Kaza, V.G., Tzudir, S., \& Proeschold-Bell, R.J. (2020). ``Enjoyment and meaning in daily activities among caregivers of orphaned and separated children in four countries.'' \emph{Children and Youth Services Review}, 116, 105103. \doi{10.1016/j.childyouth.\\2020.105103}

\item \Eagle, Kinghorn, W.A., Parnell, H.E., Amanya, C., Vann, V., Tzudir, S., Kaza, V.G., Safu, C.T., Whetten, K.A., \& Proeschold-Bell, R.J. (2019). ``Religion and caregiving for orphans and vulnerable children: A qualitative study of caregivers across four religious traditions and five global contexts.'' \emph{The Journal of Religion and Health}, 59(3):1666--1686. \doi{10.1007/s10943-019-00955-y}

\item Lutz, J.R., \& \Eagle\CS\ (2019). ``Social networks, support, and depressive symptoms: Gender differences among clergy.'' \emph{Socius} 5:2378023119873821. \doi{10.1177\\/2378023119873821}

\item Kinghorn, W.A., Keyes, C.L., Parnell, H.E., \Eagle, Biru, B.M., Amanya, C., Vann, V., Kaza, V.G., Tzudir, S., Saddo, Y.B., Whetten, K.A., \& Proeschold-Bell, R.J. (2019). ``Putting virtues in context: Engaging the VIA classification of character strengths in caregiving for orphans and vulnerable children across cultures.'' \emph{The Journal of Positive Psychology}, 14(6):845--853. \doi{10.1080/17439760.2019.1579363}

\item Proeschold-Bell, R.J., Molokwu, N.J., Keyes, C.L., Sohail, M.M., \Eagle, Parnell, H.E., Kinghorn, W.A., Amanya, C., Vann, V., Madan, I., Biru, B.M., Lewis, D., Dubie, M.E., \& Whetten, K.A. (2019). ``Caring and thriving: An international qualitative study of caregivers of orphaned and vulnerable children and strategies to sustain positive mental health.''  \emph{Children and Youth Services Review}, 98:143--153  \doi{10.1016/j.childyouth\\.2018.12.024}

\item Proeschold-Bell, R.J., Steinberg, D.R., Yao, J., \Eagle, Smith, T.W., Cai, G., \& Turner, E.L. (2018). ``Using a holistic health approach to achieve long-term weight maintenance: Results from the Spirited Life intervention.'' \emph{Translational Behavioral Medicine}, 10(1):223-233. \doi{10.1093/tbm/iby117}

\item \Eagle, \& Hybels, C.F. (2018). ``Perceived social support, received social support, and depression among clergy.'' \emph{The Journal of Social and Personal Relationships}, 36(7): 2055--2073. \doi{10.1177/0265407518776134}

\item Case, A.D., \Eagle, Yao, J., \& Proeschold-Bell, R.J. (2017). ``Disentangling race and socioeconomic status in health disparities research: An examination of Black and white clergy.'' \emph{Journal of Racial and Ethnic Health Disparities}, 5:1014--1022. \doi{10.1007/\\s40615-017-0449-7}

\item \Eagle, Keister, L,A, \& Read, J.G. (2017). ``Household charitable giving: the role of gender, marital status and religion.'' \emph{Nonprofit and Voluntary Sector Quarterly}. 47(1):185--205. \doi{10.1177/0899764017734650}

\item Proeschold-Bell, R.J., Turner, E.L., Li, X.F., Yao, J., Bennett, G.G., \Eagle, et al. (2017). ``A 2-Year holistic health and stress intervention: Results of an RCT in clergy.'' \emph{American Journal of Preventive Medicine}, 53(3):290--299. \doi{10.1016/j.amepre.2017.04.009}

\item Smith, T.W., \Eagle\CF, \& Proeschold-Bell, R.J. (2017). ``Prospective Associations between depressive symptoms and the metabolic syndrome.'' \emph{Annals of Behavioral Medicine}, 51(4): 610--619. \doi{10.1007/s12160-017-9883-3}

\item \Eagle, Miles, A.J., \& Proeschold-Bell, R.J. (2016). ``The relationship between occupational relocation and changes in mental health among clergy.'' \emph{The Review of Religious Research}, 59(1):31--45. \doi{10.1007/s13644-016-0263-4}

\item \Eagle. (2015). ``The negative relationship between size and the probability of weekly attendance in churches in the United States.'' \emph{Socius}, 2:1--10.  \doi{10.1177/2378\\023115617168}\\
Featured in the Duke Research Blog, Feb 2, 2016.

\item \Eagle. (2015). ``Historicizing the megachurch.'' \textit{The Journal of Social History}, 48:589--604. \doi{10.1093/jsh/shu109}

\item \Eagle, \& Proeschold-Bell, R.J. (2015). ``Methodological considerations in the use of name generators and interpreters." \emph{Social Networks}, 40:75--78. \doi{10.1016/j.socnet.\\2014.07.005}

\item Eagle, A.J., \Eagle, Stobbe, T.E., \& Van Kooten, K. (2015). ``Farmland protection and agricultural land values at the urban-rural fringe.'' \emph{The American Journal of Agricultural Economics}, 97:282--298. \doi{10.1093/ajae/aau098}

\item Keister, L.A. \& \Eagle. (2015). ``Religion and inequality: The role of status attainment and social balance processes." \emph{Social Thought and Research}, 33:141--174.

\item Read, J.G. \& \Eagle. (2014). ``Intersectionality and identity: An exploration of Arab American women.'' In Keister, L.A., \& Sherkat, D. (Eds.), \emph{Religion and inequality in America (pp. 75--96).} Cambridge University Press.

\item \Eagle. (2012). ``Mega, medium and mini: Size and the socio-economic status composition of American Protestant congregations.'' \emph{Research in the Sociology of Work}, 23:281--307, \doi{10.1108/S0277-2833(2012)0000023015}\\ \emph{Winner:} NC Sociological Association Graduate Student Paper Award.

\item \Eagle. (2011). ``The loosening bond of religion on Canadian society: A comment on Bibby.'' \emph{Journal for the Scientific Study of Religion}, 50(4): 838--839.

\item Read J.G., \& \Eagle. (2011). ``Intersecting identities as a source of religious incongruence.''  \emph{Journal for the Scientific Study of Religion}, 50(1): 116--132. \doi{10.1111/j.1468-5906.2010.01555.x}

\item \Eagle. (2011). ``Patterns of attendance at religious services in Canada, 1986--2008'' \emph{Journal for the Scientific Study of Religion}, 50(1): 187--200. \doi{10.1111/j.1468-5906.2010.01559.x}

\item \Eagle. (2010). ``Pneumatological ecclesiology and same-sex marriage: A non-essentialist ppproach using the work of Eugene Rogers and John Zizioulas.'' \emph{Conrad Grebel Review}, 28(2):43--68.

\item \Eagle. (2006). ``Anthony Bartlett's concept of abyssal compassion and the possibility of a truly nonviolent atonement.'' \emph{Conrad Grebel Review}, 26(2): 66--81.	

\end{enumerate}

\subsection*{Papers submitted/under revision}
\begin{enumerate} 
\item \Eagle, Mueller, C.,  Corbitt Rivers, M., \& Proeschold-Bell, R.J. ``How anti-racism policies fail: Race matching and the barriers to the economic and occupational attainment of Black pastors in the United Methodist Church.'' Conditionally accepted at \textit{The American Journal of Sociology}.

\item \Eagle. ``Casual order of burnout components in a longitudinal study of clergy.'' Manuscript submitted to the \textit{International Journal of Stress Management}.

\item Johnston, E.F., \Eagle, Headley J., \& Holleman A. ``Pastoral ministry in unsettled times: A qualitative study of the experiences of clergy during the COVID-19 pandemic.'' Manuscript submitted to \textit{Sociology of Religion}.

\item Proeschold-Bell, R.J., \Eagle, Rash, J.A. \& Tice, L. ``Evaluation of a pilot intervention to reduce stress symptoms among clergy.'' Manuscript being prepared for \textit{Stress \& Health}.

\item Proeschold-Bell, R.J., Tice, L., \Eagle, Rash, J.A., Larkins, J.S., Labrecque, S.M.  ``Protocol for a preference trial evaluating the efficacy of three interventions designed to reduce stress among clergy.'' Manuscript being prepared for \textit{BMC Open}.

\item Proeschold-Bell, R.J., Stringfield, B., Yao, J., Choi, J., \Eagle, Hybels, C., Parnell, H., Keefe, K., \& Shilling, S. ``Changes in Sabbath-keeping and mental health over time: Evaluation findings from the Sabbath Living study." Revise and resubmit \textit{Journal of Psychology and Theology}.

\end{enumerate}
\subsection*{Other Publications}
\begin{enumerate} 
\item \Eagle\ (2019). ``The Growth of the megachurch.'' In Hunt, S.J. (Ed.), \emph{Handbook of Megachurches (pp. 43--67).} Brill.

\item \Eagle\  (2018). ``Gay on God’s campus: Mobilizing for LGBT equality at Christian colleges and universities." Book review. \emph{Teaching Sociology}. Online First. \doi{10.1177/\\0092055X18814410}

\item \Eagle\ (2018). ``Theological students and educational Debt: A retrospective study of Duke Divinity School alumni, 2012--2017." Report. Duke Divinity School and the Clergy Health Initiative.

\item \Eagle\ (2017). ``Madness: American responses to mental illness, by Heather Vacek." Book review. \emph{Sociology of Religion}, 78(1): 04--105. \doi{10.1093/socrel/srx005}

\item \Eagle\ (2016). ``More people, looser ties: Social life in the megachurch.'' \emph{The Christian Century.} 133(4).

\item \Eagle\ (2013). ``Chris Scheitle and Roger Finke: Places of Faith:A Road Trip Across America's Religious Landscape." Book review.  \emph{Review of Religious Research,} 50(1): 205--206.

\item \Eagle\ (2013). ``The U.S. mainstream Protestant context.'' In Callahan, S.H. (Ed.), \emph{Religious Leadership: A Reference Handbook.} Sage Publications.
\end{enumerate}